---
title: "R Notebook"
author: "AHaotian Zhang  and APPETI YAO Wateba "
date: "21/11/20"
output: html_document
---

The code chunk appears:
```{r}
```

```{r}
library('igraph')
library('ggraph')
library('wrswoR')
```


Let's generate the initial graph
```{r}
g <- graph(edges = c(1,2,2,3,3,4,4,1), directed = TRUE,n=4)
plot(g)
```
```{r}
# To choose a vertex uniformly among existing vertices
random_unif_vertex<-function(n) sample(1:n,1,replace=T) 

# To chose random in degree based vertex
random_weigthed_vertex <- function(n,probs){ 
  s = sample(1:n,1, replace=T,prob=probs)
  return(s)
}

#function to decide if link is out or in . TRUE if OUT - FALSE if IN
choice_type <- function(p) sample(c(TRUE,FALSE),1, replace=T,prob=c(p,1-p))

```

```{r}
d = degree(g,V(g),mode='in')
probs = d / sum(d)
probs
```


# To generate our drowing random graph
```{r}
generate_graph <- function(init_graph, N=10, outprob=0.5){
    init_vertex = gorder(init_graph) +1
    for(vertex_id in init_vertex:N){
      
    
       w_c = choice_type(outprob)
        
       if(w_c) {
          d = degree(init_graph,V(init_graph),mode='in')
          probs = d / sum(d)
          choosen_vertex = random_weigthed_vertex(vertex_id - 1,probs)
          init_graph = init_graph + vertices(vertex_id)
          init_graph = init_graph + edge(vertex_id,choosen_vertex)
         
       }else {
          choosen_vertex = random_unif_vertex(vertex_id - 1)
          init_graph = init_graph + vertices(vertex_id)
          init_graph = init_graph + edge(vertex_id,choosen_vertex)
       }
    }
    
    return(init_graph)
 }
```


```{r}
```


```{r}
gen <- generate_graph(g,10000)
plot(gen)
```

# Function to plot empirical distribution
```{r}
comp_deg_dist <- function(g){
  d = degree(g,V(g),mode='in')
  return(d)
}


dist = comp_deg_dist(gen)
max_degree = max(dist)
cumul_dist = c()
for(k in 1:max_degree){
  cumul_dist <- append(cumul_dist,sum(which(dist>=k)))
}

plot(log(1:max_degree),log(cumul_dist),type = 'l',col="blue", pch="o")

```
```{r}
#let's generate many graph and plot
M = 6 # number of graphs 
size = 1000 # size of graph

```
```{r}

for (gen in 1:M){
  gen <- generate_graph(g,size)
  dist = degree(gen,V(gen),mode='in')
  max_degree = max(dist)
  cumul_dist = c()
  for(k in 1:max_degree){
    cumul_dist <- append(cumul_dist,sum(which(dist>=k)))
  }
  plot(log(1:max_degree),log(cumul_dist),type = 'l',col="blue", pch="o")
}

```

Looking at te plot of the  complementary cumulative degree distribution , We cqn see that the plot are almost a straight line 
which can lead us to think that the graphs generated degree distribution  appear to follow a power law.


To support this evidence we will plot below the distribution of graph degree.
As the degree distribution can be aproximated by a poison distribution
of parameter mu = E(k) = p(N -1)

Lets compare both distributions on same plot.

```{r}
M = 6 # number of graphs 
size = 1000

for (gen in 1:M){
  gen <- generate_graph(g,size)
  mu = centr_degree(gen,mode='in')
  mu = mu$centralization

  dist = degree(gen,V(gen),mode='in')
  max_degree = max(dist)
  eq_dist = c()
  x = 1:max_degree
  for(k in x){
    eq_dist <- append(eq_dist,sum(which(dist>=k)))
  }
  plot(x,log(eq_dist),type = 'l',col="blue", pch="o")
  lines(x,ppois(x,mu),type = 'l',col="red", pch="o")
}

```

The distribustion do not math with the poisson distribution at all so we can safely say that the graphs generated are following a power law distribution
according to what said precedently 
