---
title: "HW1_QA"
author: "Haotian Zhang  and APPETI YAO Wateba "
date: "2020/11/16"
output: html_document
---

## import libraries

```{r import libraries}

library(igraph)
library(sdpt3r)
library(Rlab)
```

## generate a random undirected graph
```{r plot graph}
B<-erdos.renyi.game(7,1/2)
plot(B)

```

## Show the Graph's all vertices and edges
```{r V E}
V(B) #vertices
E(B) #edges
```

## Get the value of opt (the size of the maximum cut we are chasing) by maxcut function in the module of "sdpt3r"
```{r maxcut}

G <- as.matrix(as_adjacency_matrix(B)) 
out<- maxcut(G)
maxcut <- abs(out$pobj)
maxcut
```


## Randomized Max-Cut Algorithm proposed by Paul Erdos
Create U as a random subset of V ; that is, for each vertex v belong to V , flip a fair coin: if Heads, add v to U otherwise do not.

From the algorithm, we can know that the probability that add v to U obeys to the Bernoulli distribution,so X={add v to U}~Ber(1,0.5).



###Build a function to extract a subset from V to U
parameters: a is the original set, b is the number you want extract
```{r}
# rbern(n,prob): Random Sample From Bernoulli Distribution 
Subset <- function(a,b){
  U<-c()
  for(k in 1:b){
    rand <- rbern(1,0.5)
    if(rand==1)
      U<-append(U,a[k])
  }
  return(U)
}
#as_ids:Convert Graph B To An Ordinary Vector
#gsize:number of edges of B
a <- as_ids(V(B))
U <-Subset(a,gsize(B))
U
```




### Evaluate the average cut-size over these M simulations and compare it with the theoretical bound opt(G)/2.

step1: get the edge of G and create the $\delta$ set.
```{r}
#lower.tri: returns a matrix of logicals the same size of a given matrix with entries TRUE in the lower or upper triangle.
G[lower.tri(G,diag=FALSE)] <-0
e<- which(G==1,arr.ind = TRUE)
colnames(e) <-c("u","v")
e
```

step2:create subset U and return its edges' number
$\delta u=\{\{u,v\}\in E such\ that\ u\in U\ and\ v\notin U\}$
```{r}
EdgeNum <-function(U,e){
  edges<-c()
  for(row in 1:nrow(e)){
    if((e[row,1] %in% U) && (!(e[row,2] %in% U))){
      edges <- append(edges, c(e[row,1],e[row,2]))
    }
  }
  return(length(edges))
}
```


step3:evaluate the average cut size over the M  simulations
```{r}
averageCutSize <- function(a,e,M){
  avg.cutsize<-c()
  for(i in 1:M){
    U<-Subset(a,length(a))
    card.u<-EdgeNum(U,e)
    avg.cutsize<-append(avg.cutsize,card.u)
  }
  return(mean(avg.cutsize))
}
```

step4:compare the average cut size with OPT(G)/2
```{r}
card <- averageCutSize(a,e ,1000)
Truecard <- maxcut/2
card
Truecard
card >= Truecard
```
*From the result, we can know that the expected size of the cut set determined by U is at least opt/2.*


## Repeat the previous algorithm and increase the size of Graph to observation if somenthing is changed 

```{r}
C <- erdos.renyi.game(50,1/3)
plot(C)
G2 <-as.matrix(as_adjacency_matrix(C))
out2 <- maxcut(G2)
maxcut2 <- abs(out2$pobj)
maxcut2
```
```{r}
a <- as_ids(V(C))
U<-Subset(a ,gsize(C))
U
```
```{r}
G2[lower.tri(G2,diag=FALSE)] <-0
e<-which(G2==1,arr.ind = TRUE)
colnames(e) <-c("u","v")
```


```{r}
Truecard2 <-maxcut2/2
Truecard2
card2 <- averageCutSize(a , e ,1000)
card2
card2 >= Truecard2
```
*From the result,when we changed the graph size,  the expected size of the cut set still determined by U is at least opt/2.*





